% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.eng.uwaterloo.ca/~djgrant
%
% (c) 2003 Samuel Tesla <samuel@alieniloquent.com> http://www.alieniloquent.com/
%
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.



\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup
\setlength{\voffset}{0in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.8]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
  \textbf{#1} & #2 \\
  \textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

%More custom commands -- ST
\newcommand{\opensourceheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
  \textbf{#1} & #2 \\
  \textit{#3} & \textit{#4} \\
\end{tabular*}}


%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Samuel Tesla}  & 402-933-5654\\
5844 Corby Street &  samuel@alieniloquent.com\\
Omaha, NE 68104 & http://www.alieniloquent.com\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\item
  \ressubheading{AIMS Community College}{Greeley, CO}
                {AA, Computer Science}{June 1999}
\item
  \ressubheading{University of Nebraska at Omaha}{Omaha, NE}
                {BS, Computer Science and Mathematics}{Expected graduation
                  in Spring of 2010}
\end{itemize}

% Work Experience

\resheading{Work Experience}
\begin{itemize}

\item
  \ressubheading{Profitstar, Inc.}{Omaha, NE}
  {Software Engineer I}{March 2004 - Present}
  \begin{itemize}
    \resitem{Design and develop software in C\# and Delphi on an eXtreme
      Programming team.}
    \resitem{Serve as a resource for agile programming methodologies.}
    \resitem{Introduce unit-tests into legacy code.}
    \resitem{Serve as a resource for unit-testing techniques.}
    \resitem{Serve as a resource for refactoring techniques.}
    \resitem{Migrated version control from Microsoft Visual Source Safe to Subversion.}
    \resitem{Developed an automated build suite for Delphi and C\# projects using Ant.}
  \end{itemize}

  \ressubheading{PayPal, Inc.}{Omaha, NE}
  {Resolution Services Agent}{Nov. 2003 - March 2004}
  \begin{itemize}
    \resitem{Respond to customer inquiries via the telephone and email
      regarding limited account access, protection services, chargebacks, and
      reversal of funds.}
    \resitem{Evaluate cases and route work to the appropriate departments.}
    \resitem{Review documentation and make decisions regarding account
      limitations.}
    \resitem{Assist in the mentoring and training of new representatives.}
  \end{itemize}

%% \item
%%   \ressubheading{Thoughtlocker.net}{Omaha, NE}
%%   {Manager}{Aug. 2002 - Present}
%%   \begin{itemize}
%%     \resitem{Design, deploy, and maintain a production web-hosting
%%       environment using Apache, Postfix, BIND, and MySQL.}
%%     \resitem{Develop and implement software tools for staff and
%%       customers using Perl and Ruby.}
%%   \end{itemize}

\item
  \ressubheading{West Interactive Corp.}{Omaha, NE}
  {Performance Assessment Coordinator}{March 2002 - Nov. 2003}
  \begin{itemize}
    \resitem{Perform historical and real-time evaluation of calls to
      ensure quality.}
    \resitem{Manage the quality and metrics of a team of
      representatives.}
    \resitem{Organize and conduct new-hire classes and post-hire
      training initiatives.}
    \resitem{Contribute to the on-going development of training
      materials.}
    \resitem{Assissted customers in the configuration and
      troubleshooting of dial-up internet connections and related
      issues.}
  \end{itemize}

%% \item
%%  \ressubheading{Sykes Enterprises Inc.}{Greeley, CO}
%%  {Customer Support Technician}{Oct. 2001 - Dec. 2001}
%%  \begin{itemize}
%%    \resitem{Assissted customers in the configuration and
%%      troubleshooting of dial-up internet connections and related
%%      issues.}
%%  \end{itemize}

\item
  \ressubheading{Experian Exactis}{Denver, CO}
  {Junior Software Development Engineer}{Sept. 2000 - Aug. 2001}
  \begin{itemize}
    \resitem{Designed and implemented CRM tool in Java.}
    \resitem{Designed and implemented user management tool in Java.}
    \resitem{Designed and implemented a log rolling tool in Perl and
      C.}
    \resitem{Designed and implemented a version verification tool in
      Perl.}
  \end{itemize}

\end{itemize}

\pagebreak

\resheading{Skills}

\begin{description}
\item[Languages:]
Objective C, C/C++, Java, Perl, Ruby, Delphi, Smalltalk, Common Lisp, PHP, \LaTeX, HTML,
CSS, JavaScript, XML, RSS
\item[Technologies:]
Cocoa, .NET, TCP/IP, unit-testing frameworks, mock objects, Ant, CruiseControl,
Rails, Subversion
\item[Operating Systems:]
Linux, Solaris, FreeBSD, Windows 95/98/NT/2000/XP, Mac OS X
\item[Miscellaneous:]
software configuration management, strong verbal and written communication
skills, excellent troubleshooting and debugging skills, strong refactoring
skills, strong unit-testing and test-driven development skills, exceptional problem solving skills, good teams skills
\end{description}

\resheading{Open Source Projects}
\begin{itemize}
\item
  \opensourceheading{OCFit}
  {http://ocfit.tigris.org}
  {Maintainer}{September 2005 - Present}
  A tool for writing acceptance tests in Objective C on Mac OS X.

\item
  \opensourceheading{RERSS}
  {http://rerss.alieniloquent.com}
  {Maintainer}{December 2002 - Present}
  A library for parsing RSS documents written in Ruby.

\item
  \opensourceheading{CGI::Session::MySQL}
  {http://raa.ruby-lang.org/list.rhtml?name=mysqlsession}
  {Maintainer}{July 2003 - Present}
  A backend module for the Ruby CGI::Session class.  It stores session data
  in a MySQL database.

\item
  \opensourceheading{ruby-pam}
  {http://ruby-pam.sourceforge.net/ruby-pam.html}
  {Patch Contributor}{July 2003}
  Fixed Ruby extension C code to use new Ruby 1.8.0 syntax.

\item
  \opensourceheading{Clive}
  {http://sourceforge.net/projects/ljclive}
  {Maintainer}{July 2001 - July 2003}
  UNIX command-line client for LiveJournal
  (http://www.livejournal.com) written in POSIX C.  It connects via
  HTTP and uses a very simple protocol to post to weblogs.
\end{itemize}
\end{document}
